---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MARMoT

<!-- badges: start -->
<!-- badges: end -->

This R package contains the function to apply MARMoT balancing technique; furthermore, it contains a function for computing the Deloof's approximation of the average rank (and also a parallelized version) and a function to compute the Absolute Standardized Bias.

## Installation

You can install the development version of MARMoT like so:

``` r
devtools::install_github("AlbertoCalore/MARMoT")
```

## Example

This is a basic example of the function "MARMoT":

```{r example}
library(MARMoT)
out = MARMoT(data = MARMoT_data, confounders = c("race", "age"), treatment = "hospital", n.cores = 1)
```


### Foundings
This package was developed within the project funded by Next Generation EU - “Age-It - Ageing well in an agening society” project (PE0000015), National Recovery and Resilience Plan (NRRP) - PE8 - Mission 4, C2, Intervention 1.3”. The views and opinions expressed are only those of the authors and do not necessarily reflect those of the European Union or the European Commission. Neither the European Union nor the European Commission can be held responsible for them. 
